Final Report

### 2022-05-06 Final Report.Rmd
renames death df cols

Import the deaths-due-to-air-pollution data
```{r}
deaths_df <- data.frame(read.csv("death-rates-from-air-pollution.csv"))
glimpse(deaths_df)
```

We are going to rename a few of the columns and glimpse the data
```{r}
colnames(deaths_df) <- c("country", "acronym", "year", "total_deaths", "indoor_deaths", "outdoor_deaths", "ozone_deaths")

>>>>

Import the deaths-due-to-air-pollution data
```{r}
deaths_df_old <- data.frame(read.csv("death-rates-from-air-pollution.csv"))
glimpse(deaths_df_old)
```
Fixed: use rename instead of colnames

We are going to rename a few of the columns and glimpse the data
```{r}
deaths_df<- deaths_df_old %>% rename(country=Entity, acronym=Code, year=Year, total_deaths=Air.pollution..total...deaths.per.100.000., indoor_deaths=Indoor.air.pollution..deaths.per.100.000., outdoor_deaths=Outdoor.particulate.matter..deaths.per.100.000., ozone_deaths=Outdoor.ozone.pollution..deaths.per.100.000.)
